Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2016-11-13 code/rmarkdown/article.Rmd
+ fix supp info figures + tables + reorder si figures and tables + update si figures and table numbers in main tex

<!-- summary of methods -->
We detected putatively adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` of the 27 plant species. We used two outlier detection methods to detect loci under selection, and they returned reasonably consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species assigned the same classification $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD; Table S1). Of the species that were associated with adaptive genetic variation, only a small proportion of loci were classified as being adaptive (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci showing strong signals of selection, we used non-metric multi-dimensional scaling (NMDS) analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a small number of continuous dimensions was needed to sufficiently describe their patterns of adaptive (all $K = `r unique(na.omit(adaptive.k))`$; Table S2) and neutral genetic variation ($K = `r min(neutral.k)`$--$`r max(neutral.k)`$; Table S1). The resulting ordinations were used to construct an adaptive (if detected) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S29--S54) generally showed substantial spatial auto-correlation (eg. _Cerastium uniflorum_, Figure S34; _Dryas octopetala_, Figures S36), suggesting that the environmental and geographic variables may prove to be effective surrogates.

@@

<!-- surrogacy analysis -->
For each species, we generated a suite of `r format(raptr.params.LST[[MODE]]$surrogacy.analysis$random.replicates, big.mark=',', scientific=FALSE)` random prioritisations, and calculated the proportion of environmental variation and adaptive (if present) genetic variation they sampled. We then repeated this process, and calculated the proportion of geographic variation and neutral genetic variation they sampled. The environmental and geographic variables were moderately effective predictors for the genetic variation represented by the randomly generated prioritisations (Figure 1). The relationship between the proportion of genetic and surrogate variation secured in the prioritisations varied among the species (species $\times$ proportion of environmental variation interaction term: ${\chi^2}_{`r env.surrogacy.AOV$df[[4]]`} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`}; P `r pvalString(env.surrogacy.AOV$Pr..Chi.[[4]])`$; species $\times$ proportion of geographic variation interaction term: ${\chi^2}_{`r round(geo.surrogacy.AOV$df[[4]],2)`} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). _Post-hoc_ analyses showed that these relationships were positive for all species (environmental: minimum \textit{z} = `r round(max(env.surrogate.spp.DF$statistic),2)`, maximum $P `r pvalString(max(env.surrogate.spp.DF$p.value))`$; geographic: minimum \textit{z} = `r round(min(geo.surrogate.spp.DF$statistic),2)`, maximum $P `r pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S4). After establishing that the the proportion of surrogate variation secured in a prioritisation also predicted the proportion of genetic variation it secured, our final step was to determine if prioritisations were more effective when generated using targets based on the surrogates.

@@

<!-- scenario analysis -->
To determine whether using environmental and geographic targets could improve the effectiveness of prioritisations in representing genetic variation, we generated prioritisations using (i) "amount targets" reflecting the traditional approach of representing a certain proportion of each species' geographic distribution, (ii) "amount and surrogate targets" where we also targeted representation of the environmental and geographic surrogates as well as a certain proportion of each species' geographic distribution, and (iii) "amount and genetic targets" where we targeted representation of the directly measured genetic variation as well as a certain proportion of each species' geographic distribution. To determine if these patterns were robust, for each of the three combinations of the targets, we generated prioritisations under four scenarios: (i) single-species with equal costs, (ii) single species with opportunity costs, (iii) multi-species with equal costs, and (iv) multi-species with opportunity costs (Figure 3, Figure SXXX).

@@

<!-- suitable targets for surrogates -->
Our results suggest that environmental and geographic surrogates can predict how much genetic variation prioritisations secure, but what targets should be used? First, our results suggest that surrogate-based targets should be used in conjunction with amount-based targets. For all species, it was possible to generate solutions that secured a high proportion of the surrogate variable (> 90 %) and only a small proportion of adaptive or neutral genetic variation (< 20 %; Figures S56--S57), and so use of amount-based targets may ameliorate this. Second, geographic surrogates may need much higher targets than environmental surrogates to capture evolutionary processes. In our analysis, geographic variation accumulated much slower for neutral genetic representation than environmental variation did with adaptive representation (Figures 2a--2b and S56--S57). To secure a representative sample of the species' neutral genetic variation ($\geq$ `r raptr.params.LST[[MODE]]$scenario.analysis$genetic.target*100` %), prioritisations needed to sample `r round(mean(surrogate.repr.prop.DF$geographic.held*100,na.rm=TRUE),2)` % $\pm$ `r round(sd(surrogate.repr.prop.DF$geographic.held*100,na.rm=TRUE),2)` SD of the variation in geographic position among the planning units occupied by the species. On the other hand, adaptive variation accumulated much faster. To secure at least `r raptr.params.LST[[MODE]]$scenario.analysis$genetic.target*100` % of each species' adaptive genetic variation, prioritisations only needed to sample on average `r round(mean(surrogate.repr.prop.DF$environmental.held*100,na.rm=TRUE),2)` % $\pm$ `r round(sd(surrogate.repr.prop.DF$environmental.held*100,na.rm=TRUE),2)` SD of the environmental conditions found across the planning units occupied by the species. Note that these proportions are based on averages across species. In many cases, higher targets may be needed to ensure that prioritisations secure a representative sample of the genetic variation for all species in a planning exercise.

<!-- adaptive genetic variation secured in prioritisations-->
Our results suggest that conservation planners can secure a reasonably representative sample of the intra-specific adaptive genetic variation using only amount-based targets. For most species, the spatial patterns of adaptive genetic variation clustered into a few distinct groups (eg. _Carex semipervens_ and _Cerastium uniflorum_; Figures S33 and S34 respectively). As a consequence, a prioritisation would only need to select a planning unit in each cluster to secure a representative sample. This mechanism explains why adaptive variation accumulated much quicker than neutral genetic variation in the randomly generated prioritisations. Additionally, this mechanism also explains why the single-species prioritisations generated using only amount targets were often able to achieve high representation--they were essentially a random selection and so frequently contained planning units in different parts of the species' ranges (Figure 4a). Overall--and contrary to our original hypotheses--it seems that conventional reserve selection methods may secure a representative sample of species' adaptive genetic variation.

@@

We used data for 27 alpine plant species in the European Alps collected by the IntraBioDiv project ([@r451]; Figure 2a). All data, code, and results are stored in an online repository (\url{www.github.com/jeffreyhanson/genetic.surrogates}) to replicate and validate this study. This data set has previously been used to explore patterns of adaptive (eg. [@r475; @r455]) and neutral genetic variation (eg. [@r478]), and to show that species richness is not an effective surrogate for genetic diversity in conservation planning ([@r486]). It was collected using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Figure S1). Project members visited every second grid cell, and if a species was detected in a cell, samples were collected from three individuals. They genotyped samples using AFLPs, and constructed matrices denoting the presence/absence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; for more information see [@r478], Table 1). Thus the data set contains information describing the genomic properties of individuals for each species present in every second grid cell. We used this data set because it comprised of comparable genetic data for a range of species with different evolutionary and life histories collected using a standardised sampling scheme, and pertained to a study area with substantial environmental variation to test the effectiveness of environmental variables.

@@

We created environmental and geographic surrogate variables for each species (see Figures S59--S561 for workflow). To describe the geographic location of each planning unit, we projected the grid into an equi-distant coordinate system (Europe Equidistant Conic; $\texttt{ESRI:102031}$), calculated the centroid of each grid cell, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each planning unit, we obtained 19 climatic layers ($30^{\prime\prime}$ resolution; [@r33]), projected them and the planning units into an equal-area coordinate system (Europe Lambert Conformal Conic; $\texttt{ESRI:102014}$), and computed planning unit averages for each climatic variable. To reduce dimensionality, for each species, we subject the climatic values associated with their planning units to a principal components analysis (PCA; Table S1). We used the first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components to characterise climatic variation found across the species' distributions inside the study area (capturing `r round(mean(spp.pca.DF[[2]]*100),2)` % $\pm$ `r round(sd(spp.pca.DF[[2]]*100),2)` SD of the total climatic variation; Figure S2). Thus we constructed a two-dimensional geographic space as a potential surrogate for neutral genetic variation, and a `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))`-dimensional environmental space as a potential surrogate for adaptive genetic variation for each species. In these spaces, each planning unit was associated with a single point. Planning units with more similar environmental conditions, or higher spatial proximity in the real world, were associated with points that were closer together in these spaces (respectively).

@@

To investigate the effectiveness of our supposed surrogates, we quantified the main spatial patterns of adaptive and neutral genetic variation (see Figures S59 and S62 for workflow). To do this, we first needed to identify which of the sampled loci were adaptive. Following best practices, we used two outlier detection methods to achieve this (an individual- and a population-level method; [@r495]). The basic premise underpinning such methods is that neutral loci are expected to exhibit a certain level of variation, and loci that deviate from this expectation are likely to be under selection ([@r480]). The advantage of these methods--in contrast to environmental association analyses--is that they do not use environmental data, which would have introduced circularity into our analysis. Loci identified as outliers in both analyses were treated as adaptive and the remainder were treated as neutral. To minimise false-positives, we omitted loci from both methods where the global frequency of the minor allele was less than 10 % and treated them as neutral.

The first outlier detection method involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} (version 2.1; [@r456]). We adopted a similar methodology to Bothwell _et al._ ([-@r455]) and applied it to each of the species separately. Following their methodology, we initially grouped conspecifics into genetic lineages to further minimise false-positives. We grouped conspecifics by fitting admixture and correlated alleles models implemented in \texttt{Structure} (version 2.3.4; [@r462]; `r structure.params.LST[[MODE]]$numruns` replicates per species; `r format(structure.params.LST[[MODE]]$admburnin, big.mark=',', scientific=FALSE)` admixture burnin iterations; `r format(structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` burnin iterations; `r format(structure.params.LST[[MODE]]$numreps+structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` total iterations) using the number of lineages previously determined by Alvarez _et al._ ([@r478]) and combining replicate runs using \texttt{ClumPP} (version 1.1.2; [@r459]; greedy algorithm based on the $G^{\prime}$ statistic; `r format(clumpp.params.LST[[MODE]]$repeats, big.mark=',', scientific=FALSE)` iterations). We then ran $\texttt{Bayescan}$ for each species using these lineages (1:1 prior odds; `r bayescan.params.LST[[MODE]]$reps` replicates per species; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r format(bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` burn-in iterations; `r format(bayescan.params.LST[[MODE]]$n+bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` total iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations) using a suitable false discovery rate ($q \leq `r bayescan.params.LST[[MODE]]$fdr`$; [@r466]). We omitted individuals if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$).

>>>>

<!-- summary of methods -->
We detected putatively adaptive genetic variation in `r as.character(as.english(length(env.surrogacy.LST)))` of the 27 plant species. We used two outlier detection methods to detect loci under selection, and they returned reasonably consistent results (mean `r round(mean(spp.outlier.methods.congruence, na.rm=TRUE),2)` % loci per species assigned the same classification $\pm$ `r round(sd(spp.outlier.methods.congruence, na.rm=TRUE),2)` SD; Table S1). Of the species that were associated with adaptive genetic variation, only a small proportion of loci were classified as being adaptive (mean `r round(mean(spp.outlier.loci.props, na.rm=TRUE),2)` % loci per species $\pm$ `r round(sd(spp.outlier.loci.props, na.rm=TRUE),2)` SD). After identifying the loci showing strong signals of selection, we used non-metric multi-dimensional scaling (NMDS) analyses to identify the main gradients of adaptive (if detected) and neutral variation for each species. Generally, only a small number of continuous dimensions was needed to sufficiently describe their patterns of adaptive (all $K = `r unique(na.omit(adaptive.k))`$; Table S2) and neutral genetic variation ($K = `r min(neutral.k)`$--$`r max(neutral.k)`$; Table S2). The resulting ordinations were used to construct an adaptive (if detected) and neutral genetic space for each species. The spatial distribution of these genetic spaces (Figures S1--S27) generally showed substantial spatial auto-correlation (eg. _Cerastium uniflorum_, Figure S6; _Dryas octopetala_, Figures S8), suggesting that the environmental and geographic variables may prove to be effective surrogates.

@@

<!-- surrogacy analysis -->
For each species, we generated a suite of `r  format(raptr.params.LST[[MODE]]$surrogacy.analysis$random.replicates, big.mark=',', scientific=FALSE)` random prioritisations, and calculated the proportion of environmental variation and adaptive (if present) genetic variation they sampled. We then repeated this process, and calculated the proportion of geographic variation and neutral genetic variation they sampled. The environmental and geographic variables were moderately effective predictors for the genetic variation represented by the randomly generated prioritisations (Figure 1; Figures S28--S29). The relationship between the proportion of genetic and surrogate variation secured in the prioritisations varied among the species (species $\times$ proportion of environmental variation interaction term: ${\chi^2}_{`r env.surrogacy.AOV$df[[4]]`} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`}; P `r pvalString(env.surrogacy.AOV$Pr..Chi.[[4]])`$; species $\times$ proportion of geographic variation interaction term: ${\chi^2}_{`r round(geo.surrogacy.AOV$df[[4]],2)`} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). _Post-hoc_ analyses showed that these relationships were positive for all species (environmental: minimum \textit{z} = `r round(max(env.surrogate.spp.DF$statistic),2)`, maximum $P `r pvalString(max(env.surrogate.spp.DF$p.value))`$; geographic: minimum \textit{z} = `r round(min(geo.surrogate.spp.DF$statistic),2)`, maximum $P `r pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S4). After establishing that the the proportion of surrogate variation secured in a prioritisation also predicted the proportion of genetic variation it secured, our final step was to determine if prioritisations were more effective when generated using targets based on the surrogates.

@@

<!-- scenario analysis -->
To determine whether using environmental and geographic targets could improve the effectiveness of prioritisations in representing genetic variation, we generated prioritisations using (i) "amount targets" reflecting the traditional approach of representing a certain proportion of each species' geographic distribution, (ii) "amount and surrogate targets" where we also targeted representation of the environmental and geographic surrogates as well as a certain proportion of each species' geographic distribution, and (iii) "amount and genetic targets" where we targeted representation of the directly measured genetic variation as well as a certain proportion of each species' geographic distribution. To determine if these patterns were robust, for each of the three combinations of the targets, we generated prioritisations under four scenarios: (i) single-species with equal costs, (ii) single species with opportunity costs, (iii) multi-species with equal costs, and (iv) multi-species with opportunity costs (Figure 3, Figure S30).

@@

<!-- suitable targets for surrogates -->
Our results suggest that environmental and geographic surrogates can predict how much genetic variation prioritisations secure, but what targets should be used? First, our results suggest that surrogate-based targets should be used in conjunction with amount-based targets. For all species, it was possible to generate solutions that secured a high proportion of the surrogate variable (> 90 %) and only a small proportion of adaptive or neutral genetic variation (< 20 %; Figures S28--S29), and so use of amount-based targets may ameliorate this. Second, geographic surrogates may need much higher targets than environmental surrogates to capture evolutionary processes. In our analysis, geographic variation accumulated much slower for neutral genetic representation than environmental variation did with adaptive representation (Figures 2a--2b and S28--S29). To secure a representative sample of the species' neutral genetic variation ($\geq$ `r raptr.params.LST[[MODE]]$scenario.analysis$genetic.target*100` %), prioritisations needed to sample `r round(mean(surrogate.repr.prop.DF$geographic.held*100,na.rm=TRUE),2)` % $\pm$ `r round(sd(surrogate.repr.prop.DF$geographic.held*100,na.rm=TRUE),2)` SD of the variation in geographic position among the planning units occupied by the species. On the other hand, adaptive variation accumulated much faster. To secure at least `r raptr.params.LST[[MODE]]$scenario.analysis$genetic.target*100` % of each species' adaptive genetic variation, prioritisations only needed to sample on average `r round(mean(surrogate.repr.prop.DF$environmental.held*100,na.rm=TRUE),2)` % $\pm$ `r round(sd(surrogate.repr.prop.DF$environmental.held*100,na.rm=TRUE),2)` SD of the environmental conditions found across the planning units occupied by the species. Note that these proportions are based on averages across species. In many cases, higher targets may be needed to ensure that prioritisations secure a representative sample of the genetic variation for all species in a planning exercise.

<!-- adaptive genetic variation secured in prioritisations-->
Our results suggest that conservation planners can secure a reasonably representative sample of the intra-specific adaptive genetic variation using only amount-based targets. For most species, the spatial patterns of adaptive genetic variation clustered into a few distinct groups (eg. _Carex semipervens_ and _Cerastium uniflorum_; Figures S5--S6). As a consequence, a prioritisation would only need to select a planning unit in each cluster to secure a representative sample. This mechanism explains why adaptive variation accumulated much quicker than neutral genetic variation in the randomly generated prioritisations. Additionally, this mechanism also explains why the single-species prioritisations generated using only amount targets were often able to achieve high representation--they were essentially a random selection and so frequently contained planning units in different parts of the species' ranges (Figure 4a). Overall--and contrary to our original hypotheses--it seems that conventional reserve selection methods may secure a representative sample of species' adaptive genetic variation.

@@

We used data for 27 alpine plant species in the European Alps collected by the IntraBioDiv project ([@r451]; Figure 2a). All data, code, and results are stored in an online repository (\url{www.github.com/jeffreyhanson/genetic.surrogates}) to replicate and validate this study. This data set has previously been used to explore patterns of adaptive (eg. [@r475; @r455]) and neutral genetic variation (eg. [@r478]), and to show that species richness is not an effective surrogate for genetic diversity in conservation planning ([@r486]). It was collected using a $20^{\prime}$ longitude by $21^{\prime}$ latitude grid (approx. 22.3 km $\times$ 25 km; Figure S31). Project members visited every second grid cell, and if a species was detected in a cell, samples were collected from three individuals. They genotyped samples using AFLPs, and constructed matrices denoting the presence/absence of polymorphisms at loci for each species (mean `r round(mean(sapply(spp.StructureData.LST, structurer:::n.loci)),2)` $\pm$ `r round(sd(sapply(spp.StructureData.LST, structurer:::n.loci)),1)` SD markers genotyped per species; for more information see [@r478], Table 1). Thus the data set contains information describing the genomic properties of individuals for each species present in every second grid cell. We used this data set because it comprised of comparable genetic data for a range of species with different evolutionary and life histories collected using a standardised sampling scheme, and pertained to a study area with substantial environmental variation to test the effectiveness of environmental variables.

@@

We created environmental and geographic surrogate variables for each species (see Figures S32--S34 for workflow). To describe the geographic location of each planning unit, we projected the grid into an equi-distant coordinate system (Europe Equidistant Conic; $\texttt{ESRI:102031}$), calculated the centroid of each grid cell, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each planning unit, we obtained 19 climatic layers ($30^{\prime\prime}$ resolution; [@r33]), projected them and the planning units into an equal-area coordinate system (Europe Lambert Conformal Conic; $\texttt{ESRI:102014}$), and computed planning unit averages for each climatic variable. To reduce dimensionality, for each species, we subject the climatic values associated with their planning units to a principal components analysis (PCA; Table S5). We used the first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components to characterise climatic variation found across the species' distributions inside the study area (capturing `r round(mean(spp.pca.DF[[2]]*100),2)` % $\pm$ `r round(sd(spp.pca.DF[[2]]*100),2)` SD of the total climatic variation; Figure S2). Thus we constructed a two-dimensional geographic space as a potential surrogate for neutral genetic variation, and a `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))`-dimensional environmental space as a potential surrogate for adaptive genetic variation for each species. In these spaces, each planning unit was associated with a single point. Planning units with more similar environmental conditions, or higher spatial proximity in the real world, were associated with points that were closer together in these spaces (respectively).

@@

To investigate the effectiveness of our supposed surrogates, we quantified the main spatial patterns of adaptive and neutral genetic variation (see Figures S32 and S35 for workflow). To do this, we first needed to identify which of the sampled loci were adaptive. Following best practices, we used two outlier detection methods to achieve this (an individual- and a population-level method; [@r495]). The basic premise underpinning such methods is that neutral loci are expected to exhibit a certain level of variation, and loci that deviate from this expectation are likely to be under selection ([@r480]). The advantage of these methods--in contrast to environmental association analyses--is that they do not use environmental data, which would have introduced circularity into our analysis. Loci identified as outliers in both analyses were treated as adaptive and the remainder were treated as neutral. To minimise false-positives, we omitted loci from both methods where the global frequency of the minor allele was less than 10 % and treated them as neutral.

The first outlier detection method involved fitting multinominal-Dirichlet models implemented in \texttt{BayeScan} (version 2.1; [@r456]). We adopted a similar methodology to Bothwell _et al._ ([-@r455]) and applied it to each of the species separately. Following their methodology, we initially grouped conspecifics into genetic lineages (Figures S36--S62). We grouped conspecifics by fitting admixture and correlated alleles models implemented in \texttt{Structure} (version 2.3.4; [@r462]; `r structure.params.LST[[MODE]]$numruns` replicates per species; `r format(structure.params.LST[[MODE]]$admburnin, big.mark=',', scientific=FALSE)` admixture burnin iterations; `r format(structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` burnin iterations; `r format(structure.params.LST[[MODE]]$numreps+structure.params.LST[[MODE]]$burnin, big.mark=',', scientific=FALSE)` total iterations) using the number of lineages previously determined by Alvarez _et al._ ([@r478]) and combining replicate runs using \texttt{ClumPP} (version 1.1.2; [@r459]; greedy algorithm based on the $G^{\prime}$ statistic; `r format(clumpp.params.LST[[MODE]]$repeats, big.mark=',', scientific=FALSE)` iterations). We then ran $\texttt{Bayescan}$ for each species using these lineages (1:1 prior odds; `r bayescan.params.LST[[MODE]]$reps` replicates per species; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r format(bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` burn-in iterations; `r format(bayescan.params.LST[[MODE]]$n+bayescan.params.LST[[MODE]]$burn, big.mark=',', scientific=FALSE)` total iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations) using a suitable false discovery rate ($q \leq `r bayescan.params.LST[[MODE]]$fdr`$; [@r466]). We omitted individuals if their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$).
